Use and acquisition of causal information for decision making under uncertainty

### 2018-05-10 Segundo_Semestre/CausalML_Workshop/Extended_Abstract.tex
mejorando lo propuesto en la intro

We model the interaction between the decision maker and his environment a repeated game with incomplete information between a player called Nature whi selects his actions from the causal model and the decision maker.

>>>>

We model the interaction between the decision maker and his environment a repeated game with incomplete information between a player called Nature which selects his actions from the causal model and the decision maker and propose a way for the agent to have \textit{beliefs} about the causal model that governs the environment.
